BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-29 tex/5-evaluation.tex
Fix/respond to some comments.
Improve figure marings and add title the the Extraction success rates table.
Minor

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{} and Goose\cite{}. Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content. These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit the fact that pages of a same blog share a similar HTML structure (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}). Readability works by .... Boilerpipe uses a very .... Goose implements a more sofisticated algorithm which ....

@@

To evaluate post content extraction 
% intro, plan

@@

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{testfigure.tex}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
The evaluation of post content extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content. These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit the fact that pages of a same blog share a similar HTML structure (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}). Readability works by .... Boilerpipe uses a very .... Goose implements a more sofisticated algorithm which ....

@@

To evaluate post content extraction
\cite{burton2011} % <- dataset
% intro, plan

@@

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{runningtimesfigure.tex}
